
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Advait Chirmule} \\ \vspace{1pt}
    \small 480-876-9732 $|$ \href{mailto:achirmul@asu.edu}{\underline{achirmul@asu.edu}} $|$ 
    \href{ https://www.linkedin.com/in/advait-chirmule }{\underline{Linkedin}}
    $|$ \href{ https://github.com/AdvaitChirmule }{\underline{Github}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Master's of Science in Computer Science, GPA: 3.80/4}{Aug 2023 -- May 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


            \resumeSubheading
                {Full Stack AI Application Intern}{May 2025 -- Nov 2025}
                {Cognia Security}{Tempe, AZ}
                \resumeItemListStart
            \resumeItem {Built a security dashboard for a startup to help clients continuously assess and fix vulnerabilities.}\resumeItem {Developed an end-to-end Spring Boot pipeline to extract asset information from Azure, normalize, enhance and store in MongoDB, with raw data archived in S3.}\resumeItem {Automated vulnerability scanning across Azure by integrating Azure Defender and OWASP tools into a CI/CD pipeline using Terraform, and generating security reports required.}\resumeItem {Managed agile workflows in Linear and used Cursor AI to enhancing coding productivity by 40\%.}\resumeItemListEnd
            \resumeSubheading
                {Research Aide}{Nov 2025 -- Dec 2025}
                {Arizona State University}{Tempe, AZ}
                \resumeItemListStart
            \resumeItem {Studied the effects of hashtags on engagement and toxicity in social media through large-scale user studies.}\resumeItem {Led experiments with 2,000+ participants, automating data collection and validation workflows with Selenium.}\resumeItem {Processed 700K+ posts using Python (Pandas, NumPy), performed sentiment analysis, and visualized statistical analysis using PowerBI.}\resumeItem {Applied Reinforcement Learning to optimize hashtag strategies, reducing toxic comments by 20\%.}\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}

\resumeSubHeadingListStart

            \resumeProjectHeading
                {\textbf{\href{https://vocabmaster.runasp.net/}{Vocab Master}} $|$ \emph{ASP.NET, C\#, JavaScript, AJAX, Kotlin, XML, Firebase}}{Jan 2025 -- Aug 2025}
                \resumeItemListStart
            \resumeItem {Built a cross-platform GRE study app serving 100+ users, enabling vocab practice and a multiplayer word game.}\resumeItem {Developed web (ASP.NET MVC) and Android versions (Android Studio) connected via Firebase RESTful APIs for secure login and game room management.}\resumeItem {Created a custom algorithm to handle network lag and maintain multiplayer game sync.}\resumeItem {Added SQL Server caching for offline functionality and to reduce latency by 60\%.}\resumeItemListEnd
            \resumeProjectHeading
                {\textbf{\href{/}{Minibase Software Modification}} $|$ \emph{Java, Linux, Algorithms, Git}}{Jan 2024 -- May 2024}
                \resumeItemListStart
            \resumeItem {Extended Minibase (Java DBMS on Linux) with column-store support and bitmap indexes, for efficient querying.}\resumeItem {Designed a custom compression algorithm using Run-Length Encoding (RLE) and Bit Stuffing, reducing storage footprint and achieving 15\% faster performance than standard RLE.}\resumeItem {Validated new features with CRUD operations and joins, successfully handling 100K rows in under 30 seconds.}\resumeItemListEnd
            \resumeProjectHeading
                {\textbf{\href{https://github.com/SER516-Clever/SER516-Team-Clever}{Taiga API Extraction}} $|$ \emph{React, FastAPI, Recharts, Node.js, Docker}}{Jan 2024 -- May 2024}
                \resumeItemListStart
            \resumeItem {Developed a Taiga project analytics tool delivering project analysis metrics to improve sprint efficiency.}\resumeItem {Built with React (frontend), Node.js middleware, and a FastAPI backend (with OAuth 2.0 for login)}\resumeItem {Achieved 80\% faster performance with Redis caching and deployed scalable, containerized services using Docker.}\resumeItem {Collaborated in Agile workflows, including sprint planning, code reviews, and daily standups, improving velocity.}\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{\href{https://ar5iv.labs.arxiv.org/html/2402.10601}{Jailbreaking Proprietary Large Language Models}} $|$ \emph{Arizona State University}}{ACL ARR 2024 Feb}
          \resumeItemListStart
            \resumeItem{Studied cryptographic ways to encode prompts to jailbreak, automated GPT API calls to speed up work by 50\%.}
            \resumeItem{Analyzed results using Power BI, achieving up to 60\% jailbreaking success across multiple large language models}
          \resumeItemListEnd

  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Python, Java, JavaScript, C\#, C++,  XML} \\
    \textbf{Frontend}{: React, HTML, CSS, RESTful API, HCI} \\
    \textbf{Backend}{: .NET, MySQL, Postgres, AWS, Docker, Kubernetes} \\
    \textbf{Others}{: Agile, Github, AI/ML, Problem Solving, Teamwork}
    }}
\end{itemize}


%-------------------------------------------
\end{document}
